---
output:
  html_document:
    theme: yeti
    highlight: espresso
    toc: true
    toc_float: false
    toc_depth: 2
---




<!-- Javascript for zooming on figures (adapted from: https://stackoverflow.com/questions/40401680) -->

<!-- Jquery import conflicts with DT::datatable so needs to be commented here -->
<!-- <script src="https://ajax.googleapis.com/ajax/libs/jquery/3.1.1/jquery.min.js"></script> -->

<style>
.zoomDiv {
  display: none;
  position: fixed;
  top: 50%;
  left: 50%;
  z-index: 50;
  transform: translate(-50%, -50%);
  background-color: #FFFFFF;
  box-shadow: 0px 0px 50px #888888;
  width: fit-content;
  max-width: 90%;
  max-height: 90%;
  overflow: auto;
}

.zoomImg {
  width: 100%;
}
</style>

<script type="text/javascript">
  $(document).ready(function() {
    $('body').prepend("<div class=\"zoomDiv\"><img src=\"\" class=\"zoomImg\"></div>");
    // onClick for all img except the zoomed one and link ones (filter)
    // use 'img.zoom' and out.extra='class=\"zoom\"' in chunk to specify manually which chunk images can be zoomed
    $('img:not(.zoomImg)').filter(':not(a *)').click(function() {
      $('.zoomImg').attr('src', $(this).attr('src'));
      $('.zoomDiv').show();
    });
    // onClick function for hiding div
    $('img.zoomImg').click(function() {
      $('.zoomDiv').hide();
    });
  });
</script>




```{r rmd_setKnitrOptions, include=FALSE}
# Set hook for PNG optimization ('optipng' must be installed on system)
#knitr::knit_hooks$set(optipng = knitr::hook_optipng)

# Set chunks default options
knitr::opts_chunk$set(results='asis',
                      echo = FALSE,           # Do not show chunks code
                      message = FALSE,        # Hide R regular text output in reports
                      warning = FALSE,        # Show warning messages
                      error = TRUE,           # Do not stop generating report on errors
                      cache = FALSE,          # Disable chunk result caching
                      cache.comments = FALSE, # Changing comments does not invalidate cache
                      fig.dim = c(10, 10),      # Size of device for R figures
                      autodep = TRUE,         # Automatic chunk dependencies if cache enabled
                      optipng = '-o2');       # PNG optimization level (2=default, 5=slow, 7=very slow)
```



```{r rmd_loadParamsAndDependencies, warning=FALSE, cache = FALSE}
### Define working folder
WORKING_DIR   = getwd();


### Load libraries, global functions/variables, and chunks
source( file.path( WORKING_DIR, "00A_Global_Dependencies.R"));

# Import chunks from source files
read_chunk( path=file.path( WORKING_DIR, "01a_TransferOfLabel_StandardSeurat.R"));
read_chunk( path=file.path( WORKING_DIR, "02_Diagnostic_after_LabelTransfer.R"));
```

```{r options, warning = TRUE, fig.dim = c(9,6)}
options(future.globals.maxSize = 8000 * 1024^2)
```
```{r, echo=FALSE,include = FALSE}
# You need this code to conduct the magic dependences attaching...
DT::datatable(matrix(),extensions = 'Buttons',  options = list(dom = 'Blfrtip', buttons = c('excel', "csv")))
```

```{r rmd_initFunctions}

### Create output directory
dir.create( PATH_ANALYSIS_OUTPUT, showWarnings = FALSE);


### Record starting time (for report and file names)
startTime = Sys.time();
startTimeReport   = format( startTime, "%Y %m %d %H:%M:%S")
startTimeFileName = format( startTime, "%Y_%m_%d_%H_%M_%S")


### Initialize utils

# Create a hash for all parameters
paramsHash = digest( environment(), algo="murmur32");

# Set seed for pseudo random number generator
set.seed(SEED);

# Set the use of multiple cores using 'future' library, as implemented in Seurat3 when possible
# https://github.com/satijalab/seurat/issues/457
plan(strategy = "multicore", workers = NBCORES);

```


---
title: `r paste( GLOBAL_DESCRIPTION, ANALYSIS_STEP_NAME, sep ="<BR>")`
---


## Run informations {.tabset .tabset-fade}

### Run
<center>
```{r rmd_runInfo_run}
pander( c( 'Date'     = startTimeReport,
           'Sample'   = EXPERIMENT_NAME,
           'Hash'     = paramsHash));
```
</center>

### Parameters
```{r rmd_runInfo_params}
listParams = as.list( paramsEnv);
pander(listParams[order(names(listParams))]); # Show params in alphabetical order
```

### System
<center>
```{r rmd_runInfo_sysInfo}
showSimpleDT( Sys.info())
```
</center>

### R
```{r rmd_runInfo_r}
pander( sessionInfo());
```

<!-- Ending the tabset section -->
<!-- ## {.toc-ignore} -->
<br /><br />




# Data analysis

## Load the data



```{r rmd_dataLoad, warning = FALSE, fig.dim = c(20,10)}
<<TransferOfLabel_StandardSeurat>>
```

```{r rmd_Diagnostic, warning = FALSE, fig.dim = c(30,10)}
<<DiagnosticAfterLabelTransfer>>
```




